Radiance - A Web Application Environment

### 2016-12-18 els2017-radiance/paper.tex
Some more minor corrections, notes

%% FIXME:
% Clarify different perspective (admin vs dev)
% Clarify "on any server setup"
% Show examples for shitty frameworks
% Focus more on new perspective rather than making the impossible possible or whatever the fuck I was thinking at the tim
% Give more code samples
% In the request cycle image, replace Application with Application/Handler
% Virual subdomains because localhost no subdomains, what fucking idiots specified this shit
% Note about lack of configuration for dev vs prod in conclusion

@@

\section{Radiance's Approach}
Radiance was designed with a different perspective in mind. Instead of viewing the application design process through the lens of the developer, it instead looks at it from the view of an administrator that would like to run an application on one of his servers. Doing so allowed it to come up with solutions to these problems that can simultaneously account for the needs of an administrator, and those of a developer. \\

@@

While the above routes are fairly simplistic in their behaviour, routes can be written to perform arbitrary operations, including stashing away data for later use during reversal. This flexibility allows things like the virtual subdomain route that is included by default. This route recognises when a request like this \texttt{/!/subdomain/foo} and maps it to \texttt{subdomain/foo}. It is necessary for the corresponding reversal route to know that the initial request was mapped by this particular route in order to appropriately translate back to the prefix, as there is no indication in the URI that we want to reverse that this should happen. \\

@@

\section{Conclusions}
By implementing the components presented in this paper, Radiance allows for an environment that can house multiple applications in the same Lisp process. It seamlessly handles both the sharing of common resources, as well as the encapsulation and separation of each application. In order to make it feasible for every application to run on any target setup, and to make it adaptable to an administrator's requirements for the public web interface, a powerful routing system was created that not only handles the incoming request, but also the outgoing data. \\

These components present clear advantages to the administrator of a system and to the developer of an application, as they simplify and streamline various parts that would otherwise be implemented ad-hoc.

>>>>

%% FIXME:
% As it stands the paper's introduction is garbage.
% Either:
%   Show examples for shitty frameworks that can't do what Radiance can
%   Focus more on the new perspective rather than making the impossible possible

@@

\section{Radiance's Approach}
Radiance was designed with a different perspective in mind. Instead of viewing the application design process through the lens of the developer, it looks at it from the view of an administrator that would like to run an application on one of his servers. Doing so allowed it to come up with solutions to these problems that can simultaneously account for the needs of an administrator, and those of a developer. \\

@@

While the above routes are fairly simplistic in their behaviour, routes can be written to perform arbitrary operations, including stashing away data for later use during reversal. This flexibility allows things like the virtual subdomain route that is included by default. This route recognises when a request like this \texttt{/!/subdomain/foo} and maps it to \texttt{subdomain/foo}. It is necessary for the corresponding reversal route to know that the initial request was mapped by this particular route in order to appropriately translate back to the prefix, as there is no indication in the URI that we want to reverse that this should happen. The virtual domain routing is especially useful on development setups, where no real domains are directly available. It allows you to use \texttt{localhost} or even just the IP address to reach everything. \\

@@

\section{Conclusions}
By implementing the components presented in this paper, Radiance allows for an environment that can conveniently house multiple applications in the same Lisp process. It seamlessly handles both the sharing of common resources, as well as the encapsulation and separation of each application. In order to make it feasible for every application to run on any target setup, and to make it adaptable to an administrator's requirements for the public web interface, a powerful routing system was created that not only handles the incoming request, but also the outgoing data. \\

These components present clear advantages to the administrator of a system and to the developer of an application, as they simplify and streamline various parts that would otherwise be implemented ad-hoc. Particularly, development and production setups can both be configured with ease.
